Output Summary

### 2021-12-16 03-post-process/output-plots.Rmd
Add diagnostics for new survival parameter

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  psi_O1_Rb_diags,
  psi_O2_Rb_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_Rb_Ra_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  stray_diags
)

>>>>

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pb_Pa_diags
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  psi_O1_Rb_diags,
  psi_O2_Rb_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_Rb_Ra_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  stray_diags
)
